Initial Analysis

### 2019-08-21 Initial_Analysis.Rmd
small changes

# Step to run function for species not computed
# Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))

# Exploited_Species <- Exploited_Species %>%
  #filter(!TaxonKey %in% Computed_Spp)

@@

# Number of cores to us 
n_cores <- detectCores()-8

@@

# Transboundary Results
Spp <- list.files(Results_Path)[1:675]

@@

Clean_Results_Trans <- Results_Trans %>%   
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(Model,
         TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(#1,2, 
    Neighbor_Territory = FishingRegion,
    #Model_Index:CT_fishing_entity,
    NT_fishing_entity= fishing_entity,
    everything()
  ) %>% 
  mutate(
    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  )

# For Carmelia
Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))

>>>>

# Step to run function for species not computed
Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))

Exploited_Species <- Exploited_Species %>%
  filter(!TaxonKey %in% Computed_Spp)

@@

# Number of cores to us 
n_cores <- detectCores()

@@

# Transboundary Results
Spp <- list.files(Results_Path)[1:672]

@@

Clean_Results_Trans <- Results_Trans %>%   
  rename(FishingRegion=Country_Territory) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(TaxonKey,
         Country_Territory= FishingRegion,
         FishingRegion=Neighbor_Territory,
         Model_Index,
         Area_Index,
         CT_fishing_entity= fishing_entity) %>% 
  left_join(Clean_sau_eez_fes,
            by = "FishingRegion") %>% 
  select(1,2, 
    Neighbor_Territory = FishingRegion,
    Model_Index:CT_fishing_entity,
    NT_fishing_entity= fishing_entity,
    everything()) %>% 
  mutate(
    CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Country_Territory),paste(CT_fishing_entity)),
    NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbor_Territory),paste(NT_fishing_entity)),
    Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
  )

# For Carmelia
#Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep=""))
